---
title: "Inbreeding"
author: "Jon"
date: "March 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("rstan")
require('bayesplot')
library("ggplot2")
require("lme4")
require("cowplot")
library(ggpubr)
#theme_set(theme_pubr())
require("loo")
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

## Read data

```{r read ID data}
data <- read.table('../data/data_147.txt')
colnames(data)<-c("StudyID","OriginalID","SpeciesID","Fragmentation","InbreedingLevel","Relic","LifeStage","Interaction","ID","SE")
N <- nrow(data)
J <- max(data$LifeStage)
M <- max(data$Fragmentation)
JM <- 4
Nsp <- max(data$SpeciesID)
L <- max(data$StudyID)
data$InbreedingLevelCont <- 0.125
index <- which(data$InbreedingLevel==2)
data$InbreedingLevelCont[index] <- 0.25
index <- which(data$InbreedingLevel==3)
data$InbreedingLevelCont[index] <- 0.5
index <- which(data$InbreedingLevel==4)
data$InbreedingLevelCont[index] <- 0.75
F <- data$InbreedingLevelCont
incidence_L <- data$LifeStage
incidence_G <- data$Fragmentation
incidence_LG <- data$Interaction
group <- data$StudyID
group_sp <- data$SpeciesID
y <- data$ID
SE <- data$SE
```
## Add partitioning data based on Fst statistics

```{r}
data.Fst<-read.table("../data/Fst_partition_data.txt",header=T,sep="\t")
data.Fst$SpeciesID <-as.numeric(data.Fst$Species)
data.Fst$kmeans<-as.numeric(data.Fst$Partition)
data.Fst$manual <- c(1,2,1,2,1,1,2,2,1,2,2,1,2,1,1,1,2,1)
data$kmeansID<-1
#data$Partition<-"Continuous"
#data$Species<-"Test"
data$manual<-data$Fragmentation
data$kmeansID<-data$Fragmentation
data$kmeansID[which(data$SpeciesID==6)]  <- 1
data$kmeansID[which(data$SpeciesID==3)]  <- 1


```

## Create interaction term area dist x life cycle

```{r}
interaction <- function(vecA,vecB){

  vecC <- (vecA-1)*4 + vecB

  return(vecC)
}

data$manual_int <- interaction(data$manual,data$LifeStage)
data$kmeansID_int <- interaction(data$kmeansID,data$LifeStage)
index <- which(data$kmeansID_int > 4)
data$kmeansID_int[index] <- 2 # baseline level
index <- which(data$manual_int > 4)
data$manual_int[index] <- 2 # baseline level
data$manual_int2 <- interaction(data$manual,data$LifeStage)
data$kmeansID_int2 <- interaction(data$kmeansID,data$LifeStage)
data$manual_int2 <- data$manual_int2 - 4

data$kmeansID_int2 <- data$kmeansID_int2 - 4
data$kmeansID_int2[which(data$kmeansID_int2 < 1)] <- 2
data$manual_int2[which(data$manual_int2 < 1)] <- 2
write.table(data,"../data/data_147_upd.txt",quote = FALSE,sep="\t")
```

## run STAN with interaction term between inbreeding level and life stage

```{r}
data$manual_int <- interaction(data$manual,data$LifeStage)
#data$kmeansID_int <- interaction(data$kmeansID,data$LifeStage)
JM <- 8
print(data$manual_int)
stan_dat1 <- list(N = N, J = J, M = M, JM = JM, Nsp = Nsp, L = L, F = F, incidence_L = incidence_L, incidence_G = data$Fragmentation, incidence_LG = data$Interaction, group = group, group_sp = group_sp, y = y, SE = SE)
set.seed(1)
fit1 <- stan(file = "model_meta_species_factor_interaction_alpha.stan", data = stan_dat1,
iter = 2000, chains = 8)
```

## Run Stan software, factor model with sum-to-zero constraint, and k-means clustering 

```{r}
data$kmeans_int <- interaction(data$kmeansID,data$LifeStage)
#data$kmeansID_int <- interaction(data$kmeansID,data$LifeStage)
JM <- 8
print(data$kmeans_int)
stan_dat2 <- list(N = N, J = J, M = M, JM = JM, Nsp = Nsp, L = L, F = F, incidence_L = incidence_L, incidence_G = data$kmeansID, incidence_LG = data$kmeans_int, group = group, group_sp = group_sp, y = y, SE = SE)
set.seed(1)
fit2 <- stan(file = "model_meta_species_factor_interaction_alpha.stan", data = stan_dat2,
iter = 1000, chains = 8)
```

## Run Stan software, mean Species effects on Fst as covariates

```{r}
data.Fst2 <- read.table("/mnt/powervault/jonhall/Desktop/SLU/data_Fst_mean_est_18.txt",sep="\t",header=T)

stan_dat3 <- list(N = N, J = J, Nsp = Nsp, L = L, F = F, incidence_L = incidence_L, group = group, group_sp = group_sp, Fst = data.Fst2$Estimate.mean, y = y, SE = SE)
set.seed(1)
fit3 <- stan(file = "model_meta_species_Fst_with_interaction_alpha.stan", data = stan_dat3,
iter = 1000, chains = 8)
```




## Save stanfit object

```{r}

saveRDS(fit1, "manual_model_sum_to_zero_alpha.rds")
saveRDS(fit2, "kmeans_model_sum_to_zero_alpha.rds")
saveRDS(fit3, "FST_model_alpha.rds")

```

## Load stanfit objects

```{r}

fit1 <- readRDS(file = "manual_model_sum_to_zero_alpha.rds")
fit2 <- readRDS(file = "kmeans_model_sum_to_zero_alpha.rds")
fit3 <- readRDS(file = "FST_model_alpha.rds")


```

## Model selection analysis using loo function


```{r model selection, echo=FALSE}
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo3 <- loo(fit3)


res <- loo_compare(loo1, loo2, loo3)
print(res)
write.table(format(res,digits=3),"../results/model_selection.txt",sep="\t",quote=FALSE)
plot(res)
#yrep <- posterior_predict(fit1)

# requires bayesplot version >= 1.5.0

```

## plots using bayesplot package

```{r}

posterior3 <- as.matrix(fit3)
p3 <- mcmc_areas(posterior3,
                 pars = c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","gamma","delta[1]","delta[2]","delta[3]","delta[4]","epsilon[1]","epsilon[2]","epsilon[3]","epsilon[4]"),
                 prob = 0.9); p3
posterior2 <- as.matrix(fit2)
p2 <- mcmc_areas(posterior2,
                 pars=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","gamma[1]","gamma[2]","delta[1]","delta[2]","delta[3]","delta[4]","delta[5]","delta[6]","delta[7]","delta[8]","epsilon[1]","epsilon[2]","epsilon[3]","epsilon[4]"),
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(alpha,beta[1],beta[2],beta[3],beta[4],gamma[1],gamma[2],delta[11],delta[21],delta[31],delta[41],delta[12],delta[22],delta[32],delta[42],epsilon[1],epsilon[2],epsilon[3],epsilon[4])) ; p2

############### test two figures instead of one #################
# prob = 0.95
p21 <- mcmc_areas(posterior2,
                 pars=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","gamma[1]","gamma[2]"),
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(alpha,beta[1],beta[2],beta[3],beta[4],gamma[1],gamma[2])); p21
p22 <- mcmc_areas(posterior2,
                 pars=c("delta[1]","delta[2]","delta[3]","delta[4]","delta[5]","delta[6]","delta[7]","delta[8]","epsilon[1]","epsilon[2]","epsilon[3]","epsilon[4]"),
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(delta[11],delta[21],delta[31],delta[41],delta[12],delta[22],delta[32],delta[42],epsilon[1],epsilon[2],epsilon[3],epsilon[4])) ; p22

p23 <- ggarrange(p21, p22,
                    labels = c("a", "b"),
                    ncol = 2, nrow = 1); p23
png("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans_v95.png")
p23
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans_v95.pdf")
p23
dev.off()
# prob = 0.9
p24 <- mcmc_areas(posterior2,
                 pars=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","gamma[1]","gamma[2]"),
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(alpha,beta[1],beta[2],beta[3],beta[4],gamma[1],gamma[2])); p24
p25 <- mcmc_areas(posterior2,
                 pars=c("delta[1]","delta[2]","delta[3]","delta[4]","delta[5]","delta[6]","delta[7]","delta[8]","epsilon[1]","epsilon[2]","epsilon[3]","epsilon[4]"),
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(delta[11],delta[21],delta[31],delta[41],delta[12],delta[22],delta[32],delta[42],epsilon[1],epsilon[2],epsilon[3],epsilon[4])) ; p25

p26 <- ggarrange(p24, p25,
                    labels = c("a", "b"),
                    ncol = 2, nrow = 1); p26
png("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans_v90.png")
p26
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans_v90.pdf")
p26
dev.off()
#postscript("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans.eps")
#p2
#dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans.png")
p2
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F_kmeans.pdf")
p2
dev.off()
posterior1 <- as.matrix(fit1)
p11 <- mcmc_areas(posterior2,
                  pars=c("a[1]","a[2]","a[3]","a[4]","a[5]","a[6]","a[7]","a[8]","a[9]","a[10]","a[11]","a[12]","a[13]","a[14]","a[15]","a[16]","a[17]","a[18]","a[19]","a[20]"),
                  prob=0.9) + 
  ggplot2::xlim(c(-0.25,0.25)); p11
# ,
p12 <- mcmc_areas(posterior2,
                  pars=c("a[21]","a[22]","a[23]","a[24]","a[25]","a[26]","a[27]","a[28]","a[29]","a[30]","a[31]","a[32]","a[33]","a[34]","a[35]","a[36]","a[37]","a[38]","a[39]","a[40]","a[41]"),
                  prob=0.9) + 
  ggplot2::xlim(c(-0.25,0.25)); p12 

figure <- ggarrange(p11, p12,
                    labels = c("a", "b"),
                    ncol = 2, nrow = 1); figure

#postscript("/mnt/powervault/jonhall/Desktop/SLU/study_effect_model2.eps")
#figure
#dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/study_effect_model2.png")
figure
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/study_effect_model2.pdf")
figure
dev.off()


names <- c("Pinus strobus",
"Pinus taeda",
"Pinus virginiana",
"Picea glauca",
"Picea abies",
"Larix decidua",
"Pinus pinaster",
"Picea omorika",
"Pinus radiata",
"Picea mariana",
"Abies alba",
"Pinus elliottii",
"Pinus sylvestris",
"Pseudotsuga menziesii",
"Pinus ponderosa",
"Abies procera",
"Pinus contorta",
"Picea pungens")
p13 <- mcmc_areas(posterior2,
                  pars=c("b[1]","b[2]","b[3]","b[4]","b[5]","b[6]","b[7]","b[8]","b[9]","b[10]","b[11]","b[12]","b[13]","b[14]","b[15]","b[16]","b[17]","b[18]"),
                  prob=0.9) + 
  ggplot2::xlim(c(-0.05,0.05)) + 
  ggplot2::scale_y_discrete(labels=c("b[1]" = names[1],
                              "b[2]" = names[2], "b[3]" = names[3],"b[4]" =names[4],"b[5]" =names[5],"b[6]" =names[6],"b[7]" =names[7],"b[8]" =names[8],"b[9]" = names[9],"b[10]" =names[10],"b[11]" = names[11],"b[12]" = names[12],"b[13]" = names[13],"b[14]" = names[14],"b[15]" = names[15],"b[16]" = names[16],"b[17]" = names[17],"b[18]" = names[18])); p13
#postscript("/mnt/powervault/jonhall/Desktop/SLU/species_effect_model2.eps")
#p13
#dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/species_effect_model2.png")
p13
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/species_effect_model2.pdf")
p13
dev.off()


p1 <- mcmc_areas(posterior1,
                 pars=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","gamma[1]","gamma[2]","delta[1]","delta[2]","delta[3]","delta[4]","delta[5]","delta[6]","delta[7]","delta[8]","epsilon[1]","epsilon[2]","epsilon[3]","epsilon[4]"), 
                 prob = 0.9)+ 
  ggplot2::scale_y_discrete(labels = expression(alpha,beta[1],beta[2],beta[3],beta[4],gamma[1],gamma[2],delta[11],delta[21],delta[31],delta[41],delta[12],delta[22],delta[32],delta[42],epsilon[1],epsilon[2],epsilon[3],epsilon[4])) ; p1
#postscript("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F.eps")
#p1
#dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F.png")
p1
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/parameters_fig_sum_to_zero_w_F.pdf")
p1
dev.off()


```
## check which posterior distributions that are different from 0 (i.e. gives an effect on ID)

```{r}
zeroinc <- function(post){
  l1 <- length(which(post >= 0))
  return(l1/length(post))
}
cat(sprintf("Parameter set: beta\n\n"))
for(i in 1:4){
  param <- paste("beta[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\n",i,zeroinc(posterior2[,param])))
}
cat(sprintf("\n\nParameter set: gamma\n\n"))
for(i in 1:2){
  param <- paste("gamma[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\n",i,zeroinc(posterior2[,param])))

}  
cat(sprintf("\n\nParameter set: delta\n\n"))
for(i in 1:8){
  param <- paste("delta[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\n",i,zeroinc(posterior2[,param])))
}
cat(sprintf("\n\nParameter set: epsilon\n\n"))
for(i in 1:4){
  param <- paste("epsilon[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\n",i,zeroinc(posterior2[,param])))
}
cat(sprintf("\n\nParameter set: study random effect (a):\n\n"))
for(i in 1:41){
  param <- paste("a[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\t",i,zeroinc(posterior2[,param])))
}
cat(sprintf("\n"))
cat(sprintf("\n\nParameter set: species random effect (a):\n\n"))
for(i in 1:18){
  param <- paste("b[",i,"]",sep="")
  cat(sprintf("P(X[%d]>0|y) = %f\t",i,zeroinc(posterior2[,param])))
}
cat(sprintf("\n"))

```


## Print posterior summaries model 1

```{r}

print(fit1,pars=c("alpha","beta","gamma","delta","epsilon","sigma_y","sigma_g","sigma_sp"),probs=c(0.025,0.5,0.975))
#extract(fit1,params)
summary1 <- summary(fit1,pars=c("alpha","beta","gamma","delta","epsilon","sigma_y","sigma_g","sigma_sp"),probs=c(0.025,0.5,0.975))$summary
print(summary1)
write.table(format(summary1,digits=2),"/mnt/powervault/jonhall/Desktop/SLU/posterior_summary_mod1.txt",sep="\t",quote=FALSE)

su5 <- summary1[,-c(2,7,8)]
su5<-su5[,c(1,3,4,2,5)]
su5<-su5[,c(1,3,4,2,5)]
write.table(format(su5,digits=2),"/mnt/powervault/jonhall/Desktop/SLU/posterior_summary_model1.txt",sep="\t",quote=FALSE)
print(fit1,pars=c("a"),probs=c(0.2,0.5,0.8))
print(fit1,pars=c("b"),probs=c(0.2,0.5,0.8))
```

## print posterior summaries model 2

```{r}
print(fit2,pars=c("mu","alpha","beta","gamma","delta","epsilon","sigma_y","sigma_g","sigma_sp"),probs=c(0.025,0.5,0.975))
summary2 <- summary(fit1,pars=c("alpha","beta","gamma","delta","epsilon","sigma_y","sigma_g","sigma_sp"),probs=c(0.025,0.5,0.975))$summary
print(summary2)
write.table(format(summary2,digits=2),"/mnt/powervault/jonhall/Desktop/SLU/posterior_summary_mod2.txt",sep="\t",quote=FALSE)

su5 <- summary2[,-c(2,7,8)]
su5<-su5[,c(1,3,4,2,5)]
su5<-su5[,c(1,3,4,2,5)]
write.table(format(su5,digits=2),"/mnt/powervault/jonhall/Desktop/SLU/posterior_summary_model2.txt",sep="\t",quote=FALSE)
print(fit2,pars=c("a"),probs=c(0.2,0.5,0.8))
print(fit2,pars=c("b"),probs=c(0.2,0.5,0.8))
```

## print posterior summaries model 3

```{r}
print(fit3,pars=c("alpha","beta","gamma","delta","epsilon","sigma_y","sigma_g","sigma_sp"))
```

## reference fixed effect model

```{r}
data$Frac<-as.factor(data$manual) 
data$Life <- as.factor(data$LifeStage)
data$Study <-as.factor(data$StudyID)
data$Species <- as.factor(data$SpeciesID)
data <- within(data, Frac <- relevel(Frac, ref = 2))
data <- within(data, Life <- relevel(Life, ref = 2))
#DF <- within(DF, b <- relevel(b, ref = 3))
lm1 <- lmer(y ~ 1 + InbreedingLevelCont + Frac + Life + Frac*Life + InbreedingLevelCont*Life + (1|Study) + (1|Species),data=data)
summary(lm1)
lm1
```

## Get predictive distributions for F = 0.5, for all life cycle stages and for both patchy (gamma index==2) and continuous (gamma index==1) populations

```{r}

#post_1 <- posterior5[,"ypred[1]"]
#parms <- "ypred[1,1]"
k <- 0 
for(i in 1:4){
  for(j in 1:2){
    name <- paste("ypred[",i,",",j,"]",sep="")
    if(k==0){
      parms <- name 
      k <- 1
    }
    else{
      parms <- c(parms,name)
    }
    cat(sprintf("P(X[%d,%d]>0|y) = %f\n",i,j,zeroinc(posterior2[,name])))
  #post_1 <- cbind(post_1,posterior5[,name])
  }   
}

p15 <-  mcmc_areas(posterior2,pars = c("ypred[1,1]","ypred[2,1]","ypred[3,1]","ypred[4,1]"), prob = 0.9,
   prob_outer = 0.99,
   point_est = "mean") + ggplot2::xlim(-0.5, 1.5); p15
p16 <-  mcmc_areas(posterior2,pars = c("ypred[1,2]","ypred[2,2]","ypred[3,2]","ypred[4,2]"), prob = 0.9,
   prob_outer = 0.99,
   point_est = "mean") + ggplot2::xlim(-0.5, 1.5); p16
ggsave("predicted_ID.pdf",p15)
ggsave("predicted_ID.png",p15)
p17 <- plot_grid(p15, p16,labels = c("a","b"),nrow=1,ncol=2,label_size = 16,rel_heights = c(1,1)); p17
png("predicted_y.png")
p17
dev.off()
df <- data.frame(posterior2[,"ypred[1,1]"]-posterior2[,"ypred[2,1]"])
df$b <- posterior2[,"ypred[1,1]"]-posterior2[,"ypred[3,1]"]
df$c <- posterior2[,"ypred[1,1]"]-posterior2[,"ypred[4,1]"]
df$d <- posterior2[,"ypred[2,1]"]-posterior2[,"ypred[3,1]"]
df$e <- posterior2[,"ypred[2,1]"]-posterior2[,"ypred[4,1]"]
df$f <- posterior2[,"ypred[3,1]"]-posterior2[,"ypred[4,1]"]
df$g <- posterior2[,"ypred[1,2]"]-posterior2[,"ypred[2,2]"]
df$h <- posterior2[,"ypred[1,2]"]-posterior2[,"ypred[3,2]"]
df$i <- posterior2[,"ypred[1,2]"]-posterior2[,"ypred[4,2]"]
df$j <- posterior2[,"ypred[2,2]"]-posterior2[,"ypred[3,2]"]
df$k <- posterior2[,"ypred[2,2]"]-posterior2[,"ypred[4,2]"]
df$l <- posterior2[,"ypred[3,2]"]-posterior2[,"ypred[4,2]"]
df$m <- posterior2[,"ypred[1,1]"]-posterior2[,"ypred[1,2]"]
colnames(df)[1]<-"a"
prop.a <- length(which(df$a>0))/length(df$a)
prop.b <- length(which(df$b>0))/length(df$b)
prop.c <- length(which(df$c>0))/length(df$c)
prop.d <- length(which(df$d>0))/length(df$d)
prop.e <- length(which(df$e>0))/length(df$e)
prop.f <- length(which(df$f>0))/length(df$f)
prop.g <- length(which(df$g>0))/length(df$g)
prop.h <- length(which(df$h>0))/length(df$h)
prop.i <- length(which(df$i>0))/length(df$i)
prop.j <- length(which(df$j>0))/length(df$j)
prop.k <- length(which(df$k>0))/length(df$k)
prop.l <- length(which(df$l>0))/length(df$l)
prop.m <- length(which(df$m>0))/length(df$m)
print(fit2,pars=c("ypred"))
```



## comparing interactions all

```{r}
df <- data.frame(posterior2[,"delta[1]"]-posterior2[,"delta[2]"])
df$b <- posterior2[,"delta[1]"]-posterior2[,"delta[3]"]
df$c <- posterior2[,"delta[1]"]-posterior2[,"delta[4]"]
df$d <- posterior2[,"delta[2]"]-posterior2[,"delta[3]"]
df$e <- posterior2[,"delta[2]"]-posterior2[,"delta[4]"]
df$f <- posterior2[,"delta[3]"]-posterior2[,"delta[4]"]
df$g <- posterior2[,"delta[5]"]-posterior2[,"delta[6]"]
df$h <- posterior2[,"delta[5]"]-posterior2[,"delta[7]"]
df$i <- posterior2[,"delta[5]"]-posterior2[,"delta[8]"]
df$j <- posterior2[,"delta[6]"]-posterior2[,"delta[7]"]
df$k <- posterior2[,"delta[6]"]-posterior2[,"delta[8]"]
df$l <- posterior2[,"delta[7]"]-posterior2[,"delta[8]"]
df$beta0 <- data.frame(posterior2[,"beta[1]"]-posterior2[,"beta[2]"])
df$beta1 <- posterior2[,"beta[1]"]-posterior2[,"beta[3]"]
df$beta2 <- posterior2[,"beta[1]"]-posterior2[,"beta[4]"]
df$beta4 <- posterior2[,"beta[2]"]-posterior2[,"beta[3]"]
df$beta5 <- posterior2[,"beta[2]"]-posterior2[,"beta[4]"]
df$beta6 <- posterior2[,"beta[3]"]-posterior2[,"beta[4]"]
df$gamma <- data.frame(posterior2[,"gamma[1]"]-posterior2[,"gamma[2]"])
df$epsilon0 <- data.frame(posterior2[,"epsilon[1]"]-posterior2[,"epsilon[2]"])
df$epsilon1 <- posterior2[,"epsilon[1]"]-posterior2[,"epsilon[3]"]
df$epsilon2 <- posterior2[,"epsilon[1]"]-posterior2[,"epsilon[4]"]
df$epsilon4 <- posterior2[,"epsilon[2]"]-posterior2[,"epsilon[3]"]
df$epsilon5 <- posterior2[,"epsilon[2]"]-posterior2[,"epsilon[4]"]
df$epsilon6 <- posterior2[,"epsilon[3]"]-posterior2[,"epsilon[4]"]

colnames(df)[1] <- "a"
prop.a <- length(which(df$a>0))/length(df$a)
prop.b <- length(which(df$b>0))/length(df$b)
prop.c <- length(which(df$c>0))/length(df$c)
prop.d <- length(which(df$d>0))/length(df$d)
prop.e <- length(which(df$e>0))/length(df$e)
prop.f <- length(which(df$f>0))/length(df$f)
prop.g <- length(which(df$g>0))/length(df$g)
prop.h <- length(which(df$h>0))/length(df$h)
prop.i <- length(which(df$i>0))/length(df$i)
prop.j <- length(which(df$j>0))/length(df$j)
prop.k <- length(which(df$k>0))/length(df$k)
prop.l <- length(which(df$l>0))/length(df$l)
prop.b0 <- length(which(df$beta0>0))/length(df$beta0)
prop.b1 <- length(which(df$beta1>0))/length(df$beta1)
prop.b2 <- length(which(df$beta2>0))/length(df$beta2)
prop.b3 <- length(which(df$beta3>0))/length(df$beta3)
prop.b4 <- length(which(df$beta4>0))/length(df$beta4)
prop.b5 <- length(which(df$beta5>0))/length(df$beta5)
prop.b6 <- length(which(df$beta6>0))/length(df$beta6)
prop.t <- length(which(df$t>0))/length(df$t)
prop.u <- length(which(df$u>0))/length(df$u)
prop.v <- length(which(df$v>0))/length(df$v)
prop.w <- length(which(df$w>0))/length(df$w)
prop.x <- length(which(df$x>0))/length(df$x)
prop.y <- length(which(df$y>0))/length(df$y)
prop.z <- length(which(df$z>0))/length(df$z)
prop.a2 <- length(which(df$a2>0))/length(df$a2)
prop.a3 <- length(which(df$a3>0))/length(df$a3)
```

## Plot posterior distribution comparison

```{r}
# Basic histogram
df <- data.frame(posterior2[,"beta[1]"]-posterior2[,"beta[2]"])
df$b <- posterior2[,"beta[1]"]-posterior2[,"beta[3]"]
df$c <- posterior2[,"beta[1]"]-posterior2[,"beta[4]"]
df$d <- posterior2[,"beta[2]"]-posterior2[,"beta[3]"]
df$e <- posterior2[,"beta[2]"]-posterior2[,"beta[4]"]
df$f <- posterior2[,"beta[3]"]-posterior2[,"beta[4]"]
colnames(df)[1] <- "a"
prop.a <- length(which(df$a>0))/length(df$a)
prop.b <- length(which(df$b>0))/length(df$b)
prop.c <- length(which(df$c>0))/length(df$c)
prop.d <- length(which(df$d>0))/length(df$d)
prop.e <- length(which(df$e>0))/length(df$e)
prop.f <- length(which(df$f>0))/length(df$f)
df2 <- data.frame(posterior2[,"gamma[1]"]-posterior2[,"gamma[2]"])
colnames(df2)[1] <- "a"
prop2 <- length(which(df2$a>0))/length(df2$a)
p0 <- ggplot(df2,aes(x=a)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
  geom_text(x=0.25, y=400, label = expression(paste("p(",gamma[1]," - ",gamma[2]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
  # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  geom_text(x=0.25, y=360, label = prop2,size=5) +
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p0
pdf("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_gamma.pdf")
p0
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_gamma.png")
p0
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_gamma.eps")
p0
dev.off()
p1 <- ggplot(df,aes(x=a)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
 # geom_text(x=0.15, y=400, label = expression(paste("p(",beta[1]," - ",beta[2]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
  # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
#  geom_text(x=0.15, y=350, label = prop.a,size=5) +
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p1
p2 <- ggplot(df,aes(x=d)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
 # geom_text(x=0.15, y=250, label = expression(paste("p(",beta[2]," - ",beta[3]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
#  geom_text(x=0.15, y=200, label = prop.d,size=5) +
  # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p2

p3 <- ggplot(df,aes(x=b)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
 # geom_text(x=0.15, y=400, label = expression(paste("p(",beta[1]," - ",beta[3]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
#geom_text(x=0.15, y=350, label = prop.b,size=5) +
    # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p3
p4 <- ggplot(df,aes(x=e)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
 # geom_text(x=-0.4, y=350, label = expression(paste("p(",beta[2]," - ",beta[4]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) =
#  geom_text(x=-0.4, y=300, label = prop.e,size=5) + # ",prop.a,sep="")
  # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p4

p5 <- ggplot(df,aes(x=c)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
 # geom_text(x=0.6, y=360, label = expression(paste("p(",beta[1]," - ",beta[4]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
 #geom_text(x=0.6, y=300, label = prop.c,size=5) +  # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p5
p6 <- ggplot(df,aes(x=f)) +
  geom_histogram(fill="white", color="black")+
  geom_vline(aes(xintercept=0), color="blue",
             linetype="dashed",size=1.3)+
  labs(x="Effect size", y = "Counts")+
  theme_classic()+
#  geom_text(x=0.3, y=340, label = expression(paste("p(",beta[3]," - ",beta[4]," > 0 | y) = ",sep="")),size=5,aes(fontface=3)) + # paste("p(x1 - x2 > 0 | y) = ",prop.a,sep="")
 #  geom_text(x=0.3, y=280, label = prop.f,size=5) + # label=bquote("p(" ~ beta[1]-beta[2]>0 ~ "|y) == " ~ prop.a)
  theme(axis.text=element_text(size=14,color="black"),axis.title=element_text(size=14,color="black")); p6
p7 <- plot_grid(p1, p3,labels = c("a","b"),nrow=2,ncol=1,label_size = 16,rel_heights = c(1,1)); p7
pdf("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_1.pdf")
p7
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_1.png")
p7
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_1.eps")
p7
dev.off()
p8 <- plot_grid(p5, p2,labels = c("c","d"),nrow=2,ncol=1,label_size = 16,rel_heights = c(1,1)); p8
pdf("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_2.pdf")
p8
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_2.png")
p8
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_2.eps")
p8
dev.off()
p9 <- plot_grid(p4, p6,labels = c("e","f"),nrow=2,ncol=1,label_size = 16,rel_heights = c(1,1)); p9
pdf("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_3.pdf")
p9
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_3.png")
p9
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta_3.eps")
p9
dev.off()

figure <- ggarrange(p1, p5, p4, p3, p2, p6,
                    labels = c("a", "c", "e", "b", "d", "f"),
                    ncol = 3, nrow = 2)
figure
pdf("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta.pdf")
figure
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta.png")
figure
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/compare_posteriors_beta.eps")
figure
dev.off()

```

