---
title: "Inbreeding"
author: "Jon"
date: "March 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("bayesplot")
library("ggplot2")
require("rstan")
require("stats")
require("cowplot")
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```

## Read Fst data

```{r read data}
#Fst <- read.table("../data/Fst_estimates.txt",header = T,sep="\t")
#index <- which(Fst$Type.of.marker=="chloroplast" | Fst$Type.of.marker=="mitocondrial")
#Fst <- Fst[-index,]
#Fst$Marker.type2 <- 0
#index <- which(Fst$Marker.type=='AFLP' | Fst$Marker.type=='RAPD')
#Fst$Marker.type2[index]<-1
#index <- which(Fst$Marker.type=='SNP')
#Fst$Marker.type2[index]<-2
#index <- which(Fst$Marker.type=='SSR')
#Fst$Marker.type2[index]<-3
#index <- which(Fst$Marker.type=='Allozymes' | Fst$Marker.type=='Isozymes')
#Fst$Marker.type2[index]<-4

Fst <- read.table("../data/data_Fst_18sp.txt",header = T,sep="\t")
y <- Fst$Fst
n <- as.numeric(length(y))
x1 <- as.numeric(Fst$Species)
x2 <- Fst$Marker.type2
nlev1 <- max(x1)
nlev2 <- max(x2)
Fst2 <- read.table("data_Fst.txt",header = T,sep="\t")
y2 <- Fst2$Fst
n2 <- as.numeric(length(y2))
x12 <- as.numeric(Fst2$Species)
x22 <- Fst2$Marker.type2
nlev12 <- max(x12)
nlev22 <- max(x22)
index <- which(Fst$Marker.type=='AFLP' | Fst$Marker.type=='RAPD')
Fst3 <- Fst[-index,]
y3 <- Fst3$Fst
n3 <- as.numeric(length(y3))
x13 <- as.numeric(Fst3$Species)
x23 <- Fst3$Marker.type2
nlev13 <- max(x13)
nlev23 <- max(x23)
```

## Including Plots

You can also embed plots, for example:

```{r data check, echo=FALSE}
par(mfrow=c(1,3))
h1<-hist(Fst$Fst,nclass = 15,xlab = "Fst",main = "untransformed")
h2 <- hist(log(Fst$Fst),nclass = 15,xlab="log(Fst)",main = "log transformed")
h3 <- hist(sqrt(Fst$Fst),nclass = 15,xlab="sqrt(Fst)",main = "square-root transformed")
#pdf("../results/dist_Fst.pdf")
#h1
#h2
#h3
#dev.off()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
stan_code <- "
data {
int n;
int nlev1;
int nlev2;
int x1[n];
int x2[n];
vector<lower=0, upper=1>[n] y;
}
parameters {
vector[nlev1-1] alpha[2];
vector[nlev2-1] beta[2];
vector[2] inter; // intercept
}
transformed parameters {
vector[nlev1] alpha_tr[2];
vector[nlev2] beta_tr[2];
vector<lower=0, upper=1>[n] mu;
vector<lower=0>[n] phi;
vector[n] p;
vector[n] q;
for (i in 1:(nlev1-1)){
  for (j in 1:2){
    alpha_tr[j,i] = alpha[j,i];
  }
}
for (i in 1:(nlev2-1)){
  for (j in 1:2){
    beta_tr[j,i] = beta[j,i];
  }
}
for (i in 1:2){
alpha_tr[i,nlev1] = -sum(alpha[i,]);
beta_tr[i,nlev2] = -sum(beta[i,]);
}
for (i in 1:n) {
mu[i] = inv_logit(inter[1] + alpha_tr[1,x1[i]] + beta_tr[1,x2[i]]);
phi[i] = exp(inter[2] +alpha_tr[2,x1[i]] + beta_tr[2,x2[i]]);
p[i] = mu[i] * phi[i];
q[i] = phi[i] - mu[i] * phi[i];
}
}
model {
y ~ beta(p, q);
for (i in 1:nlev1){
  for (j in 1:2){
    alpha_tr[j,i] ~ normal(0,2);
  }
}
for (i in 1:nlev2){
  for (j in 1:2){
    beta_tr[j,i] ~ normal(0,2);
  }
}
for (j in 1:2){
  inter[j] ~ normal(0,2);
}
}"
it_per_chain <- 1000
nchain <- 8
stan_dat <- list(n = n, nlev1 = nlev1, nlev2 = nlev2, x1 = x1, x2 = x2, y = y)
set.seed(1)
fit <- stan(model_code = stan_code, data = stan_dat,
iter = it_per_chain, chains = nchain)

```
## model with 21 species

```{r}
stan_dat2 <- list(n = n2, nlev1 = nlev12, nlev2 = nlev22, x1 = x12, x2 = x22, y = y2)
set.seed(1)
fit2 <- stan(model_code = stan_code, data = stan_dat2,
iter = it_per_chain, chains = nchain)
```

## model analysing data without AFLP/RAPD based Fst estimates

```{r}
stan_dat3 <- list(n = n3, nlev1 = nlev13, nlev2 = nlev23, x1 = x13, x2 = x23, y = y3)
set.seed(1)
fit3 <- stan(model_code = stan_code, data = stan_dat3,
iter = it_per_chain, chains = nchain)
```

## Analyze results
```{r}
#fit_summary <- summary(fit)
#print(round(fit_summary$summary,digits = 2))
#fit_summary2 <- summary(fit2)
#print(round(fit_summary2$summary,digits = 2))
mu_tau_summary <- summary(fit, pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]","beta_tr[1,4]"), probs = c(0.05,0.5, 0.95))$summary
print(mu_tau_summary)
#mu_tau_summary <- summary(fit2, pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]","beta_tr[1,4]"), probs = c(0.05,0.5, 0.95))$summary
print(mu_tau_summary)
mu_tau_summary <- summary(fit3, pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]"), probs = c(0.05,0.5, 0.95))$summary
print(mu_tau_summary)

posterior <- as.matrix(fit)
posterior2 <- as.matrix(fit2)
posterior3 <- as.matrix(fit3)
p1 <- mcmc_areas(posterior,pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]","beta_tr[1,4]"),prob = 0.9)+ scale_y_discrete(labels=c("beta_tr[1,1]" = "ALFP/RAPD", "beta_tr[1,2]" = "SNP",
                              "beta_tr[1,3]" = "SSR", "beta_tr[1,4]" = "Isozymes/Allozymes"))
#p1
p12 <- mcmc_areas(posterior2,pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]","beta_tr[1,4]"),prob = 0.9)+ scale_y_discrete(labels=c("beta_tr[1,1]" = "ALFP/RAPD", "beta_tr[1,2]" = "SNP",
                              "beta_tr[1,3]" = "SSR", "beta_tr[1,4]" = "Isozymes/Allozymes"))
#p12
p13 <- mcmc_areas(posterior3,pars = c("beta_tr[1,1]","beta_tr[1,2]","beta_tr[1,3]"),prob = 0.9)+ scale_y_discrete(labels=c("beta_tr[1,1]" = "SNP",
                              "beta_tr[1,2]" = "SSR", "beta_tr[1,3]" = "Isozymes/Allozymes"))
p13
p2 <- mcmc_areas(posterior,pars = c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]"),prob = 0.9)+ scale_y_discrete(labels=c("alpha_tr[1,1]" = "Picea mariana",
                              "alpha_tr[1,2]" = "Picea pungens", "alpha_tr[1,3]" = "Pseudotsuga menziesii","alpha_tr[1,4]" ="Larix decidua","alpha_tr[1,5]" ="Pinus taeda","alpha_tr[1,6]" ="Pinus contorta","alpha_tr[1,7]" ="Pinus pinaster","alpha_tr[1,8]" ="Abies procera","alpha_tr[1,9]" = "Picea abies","alpha_tr[1,10]" ="Pinus ponderosa","alpha_tr[1,11]" = "Pinus radiata","alpha_tr[1,12]" = "Pinus sylvestris","alpha_tr[1,13]" = "Picea omorika","alpha_tr[1,14]" = "Abies alba","alpha_tr[1,15]" = "Pinus elliottii","alpha_tr[1,16]" = "Pinus virginiana","alpha_tr[1,17]" = "Pinus monticola","alpha_tr[1,18]" = "Picea glauca"))
#
p22 <- mcmc_areas(posterior2,pars = c("alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]","alpha_tr[1,19]","alpha_tr[1,20]","alpha_tr[1,21]"),prob = 0.9)+ scale_y_discrete(labels=c("alpha_tr[1,2]" = "Picea mariana",
                              "alpha_tr[1,3]" = "Picea pungens", "alpha_tr[1,4]" = "Pseudotsuga menziesii","alpha_tr[1,5]" ="Larix decidua","alpha_tr[1,7]" ="Pinus taeda","alpha_tr[1,8]" ="Pinus contorta","alpha_tr[1,9]" ="Pinus pinaster","alpha_tr[1,10]" ="Abies procera","alpha_tr[1,11]" = "Picea abies","alpha_tr[1,13]" ="Pinus ponderosa","alpha_tr[1,14]" = "Pinus radiata","alpha_tr[1,15]" = "Pinus sylvestris","alpha_tr[1,16]" = "Picea omorika","alpha_tr[1,17]" = "Abies alba","alpha_tr[1,18]" = "Pinus elliottii","alpha_tr[1,19]" = "Pinus virginiana","alpha_tr[1,20]" = "Pinus monticola","alpha_tr[1,21]" = "Picea glauca"))
p23 <- mcmc_areas(posterior3,pars = c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]"),prob = 0.9)+ scale_y_discrete(labels=c("alpha_tr[1,1]" = "Picea mariana",
                              "alpha_tr[1,2]" = "Picea pungens", "alpha_tr[1,3]" = "Pseudotsuga menziesii","alpha_tr[1,4]" ="Larix decidua","alpha_tr[1,5]" ="Pinus taeda","alpha_tr[1,6]" ="Pinus contorta","alpha_tr[1,7]" ="Pinus pinaster","alpha_tr[1,8]" ="Abies procera","alpha_tr[1,9]" = "Picea abies","alpha_tr[1,10]" ="Pinus ponderosa","alpha_tr[1,11]" = "Pinus radiata","alpha_tr[1,12]" = "Pinus sylvestris","alpha_tr[1,13]" = "Picea omorika","alpha_tr[1,14]" = "Abies alba","alpha_tr[1,15]" = "Pinus elliottii","alpha_tr[1,16]" = "Pinus virginiana","alpha_tr[1,17]" = "Pinus monticola","alpha_tr[1,18]" = "Picea glauca"))

p12
p22
p23
png("../results/marker_type_wo_AFLP_RAPD.png")
p13
dev.off()
pdf("../results/marker_type_wo_AFLP_RAPD.pdf")
p13
dev.off()
png("../results/marker_type.png")
p1
dev.off()
#postscript("../results/marker_type.eps")
#p1
#dev.off()
png("../results/marker_type_2.png")
p12
dev.off()
pdf("../results/marker_type.pdf")
p1
dev.off()
png("../results/Species_Fst.png")
p22
dev.off()
#postscript("../results/Species_Fst_wo_AFLP_RAPD.eps")
#p23
#dev.off()
png("../results/Species_Fst_wo_AFLP_RAPD.png")
p23
dev.off()
pdf("../results/Species_Fst_wo_AFLP_RAPD.pdf")
p23
dev.off()
#draws <- draws[, c("alpha[2]", "alpha[3]")]
#colnames(draws) <- c("Species", "Marker")
#mcmc_hist(draws, facet_args = list(labeller = label_parsed)) +
#ggtitle("Posterior densities for slope coefficients") +
#theme_light()
names <- c("Pinus strobus",
"Pinus taeda",
"Pinus virginiana",
"Picea glauca",
"Picea abies",
"Larix decidua",
"Pinus pinaster",
"Picea omorika",
"Pinus radiata",
"Picea mariana",
"Abies alba",
"Pinus elliottii",
"Pinus sylvestris",
"Pseudotsuga menziesii",
"Pinus ponderosa",
"Abies procera",
"Pinus contorta",
"Picea pungens")
```

`
## Clustering based on estimated posterior distributions of species effect on Fst



```{r generate clusters partitioning}
niter <- 10000 # number 
list_of_draws <- extract(fit)
#list_of_draws2 <- extract(fit2)
#list_of_draws3 <- extract(fit3)
print(names(list_of_draws))
head(list_of_draws$alpha_tr)
cat(sprintf('dim(alpha_tr) = %dx%d\n',dim(list_of_draws$alpha_tr)[1],dim(list_of_draws$alpha_tr)[2]))
#head(posterior)
alpha.post<-posterior[, c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]")]
alpha.post2<-posterior2[, c("alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]","alpha_tr[1,19]","alpha_tr[1,20]","alpha_tr[1,21]")]
alpha.post3<-posterior3[, c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]")]
ntot <- it_per_chain*nchain/2
generate_figure <- function(alpha.post,ntot,nlev1,niter,control){
  tmp <- rep(0,nlev1)
  res.tot <- rep(0,nlev1)
  for (i in 1:niter){ 
    for (j in 1:nlev1){
      r1 <- sample(ntot,1)
   # cat(sprintf('ntot = %d\nr1 = %d\ndim(alpha.post) = %d x %d\n',ntot,r1,dim(alpha.post)[1],dim(alpha.post)[2]))
      tmp[j]<-alpha.post[r1,j] 
    }
    res<-kmeans(tmp,2)
 # if(res$cluster[16]==2)
    index <- which(res$cluster==res$cluster[control])
    res.tot[index] <-res.tot[index]+1 
  #print(res$cluster)
  }
  res.tot<-res.tot/niter
  res.tot<-as.data.frame(res.tot)

  #res.tot$Species <- c("Picea mariana", "Picea pungens",  "Pseudotsuga menziesii","Larix decidua","Pinus taeda","Pinus contorta","Pinus pinaster","Abies procera", "Picea abies","Pinus ponderosa", "Pinus radiata", "Pinus sylvestris", "Picea omorika","Abies alba","Pinus elliottii","Pinus virginiana", "Pinus monticola", "Picea glauca")
res.tot$Species <- c("Picea mariana","Picea pungens","Pseudotsuga menziesii","Larix decidua","Pinus taeda","Pinus contorta","Pinus pinaster","Abies procera","Picea abies","Pinus ponderosa","Pinus radiata","Pinus sylvestris","Picea omorika","Abies alba","Pinus elliottii","Pinus virginiana","Pinus monticola","Picea glauca")
  colnames(res.tot)[1] <-"Proportion"
  index<-which(res.tot$Proportion<0.5)
  res.tot$Partition<-"Fragmented"
  res.tot$Partition[index]<-"Well-connected"
  return(res.tot)
}
res.tot<-generate_figure(alpha.post,ntot,nlev1,niter,13)
res.tot2<-generate_figure(alpha.post2,ntot,nlev1,niter,13)
res.tot3<-generate_figure(alpha.post3,ntot,nlev1,niter,13)
mu_tau_summary <- summary(fit, pars = c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]"), probs = 0.5)$summary
res.tot$Mean <- mu_tau_summary[,1]
res.tot$MeanSTD <- scale(mu_tau_summary[,1])
#mu_tau_summary <- summary(fit2, pars = c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]"), probs = 0.5)$summary
#res.tot2$Mean <- mu_tau_summary[,1]
#res.tot2$MeanSTD <- scale(mu_tau_summary[,1])
mu_tau_summary <- summary(fit3, pars = c("alpha_tr[1,1]","alpha_tr[1,2]","alpha_tr[1,3]","alpha_tr[1,4]","alpha_tr[1,5]","alpha_tr[1,6]","alpha_tr[1,7]","alpha_tr[1,8]","alpha_tr[1,9]","alpha_tr[1,10]","alpha_tr[1,11]","alpha_tr[1,12]","alpha_tr[1,13]","alpha_tr[1,14]","alpha_tr[1,15]","alpha_tr[1,16]","alpha_tr[1,17]","alpha_tr[1,18]"), probs = 0.5)$summary
res.tot3$Mean <- mu_tau_summary[,1]
res.tot3$MeanSTD <- scale(mu_tau_summary[,1])
```

## Plot partitions results

```{r}
p <- ggplot(data=res.tot,aes(x = reorder(Species,Proportion),y = Proportion,fill=Partition))   +
  geom_bar(stat="identity", color="black") + coord_flip() + geom_hline(yintercept=0.5,linetype=1,size=1.3)+theme(axis.text=element_text(size=12,color="black"),axis.title=element_text(size=14,color="black"),legend.text=element_text(size=12,color="black"),legend.title=element_text(size=14,color="black"),axis.title.y=element_blank())
p
p2 <- ggplot(data=res.tot2,aes(x = reorder(Species,Proportion),y = Proportion,fill=Partition))   +
  geom_bar(stat="identity", color="black") + coord_flip() + geom_hline(yintercept=0.5,linetype=1,size=1.3)+theme(axis.text=element_text(size=12,color="black"),axis.title=element_text(size=14,color="black"),legend.text=element_text(size=12,color="black"),legend.title=element_text(size=14,color="black"),axis.title.y=element_blank())
p2
p3 <- ggplot(data=res.tot3,aes(x = reorder(Species,Proportion),y = Proportion,fill=Partition))   +
  geom_bar(stat="identity", color="black") + coord_flip() + geom_hline(yintercept=0.5,linetype=1,size=1.3)+theme(axis.text=element_text(size=8,color="black"),axis.title=element_text(size=14,color="black"),legend.text=element_text(size=12,color="black"),legend.title=element_text(size=14,color="black"),axis.title.y=element_blank())
p3
postscript("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition.eps")
p
dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition.pdf")
p
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition.png")
p
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition2.png")
p2
dev.off()
postscript("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition_wo_AFLP.eps")
p3
dev.off()

#p6 <- plot_grid(p1, p, p22,labels = #c("a","c","b"),nrow=3,ncol=1,label_size = 10); p6
p7 <- plot_grid(p13, p3,labels = c("a","b"),nrow=2,ncol=1,label_size = 16,rel_heights = c(1,1.9)); p7
#postscript("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition_wo_AFLP.eps")
#p7
#dev.off()
pdf("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition_wo_AFLP.pdf")
p7
dev.off()
png("/mnt/powervault/jonhall/Desktop/SLU/barplot_partition_wo_AFLP.png")
p7
dev.off()
```
## Save data to file

```{r}
write.table(res.tot3,"Fst_partition_data.txt",quote=F,sep="\t",row.names = F)
```

